Summer 2025 ToDo

### 2025-05-30 Relations/Paper/Implications.tex
Counterexamples badly numbered. Only halfway fixed!
Counterexmples updated in table. DOUBLE CHECK

\begin{table}[h!]
    \centering
    \renewcommand\arraystretch{1.2}
    \begin{tabular}{!{\vrule width 1.5pt}
        >{\columncolor{gray!30}}l
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}}
        \Xhline{1.5pt}
        \rowcolor{gray!30} 
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SMandWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SN$} \\
        \Xhline{1.5pt}
        $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:12} & CE-\ref{CE:4} & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
        \hline
        $\NP$ & CE-\ref{CE:10} & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\MP$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[2] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\CR$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$ & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$ & $\SN$ \\
        \hline
        \Xhline{1.5pt}
    \end{tabular}
    \caption{Local implications}
\end{table}

\vspace{-1cm}
% \\[-0.5cm]
\begin{table}[h!]
    \centering
    \renewcommand\arraystretch{1.2}
    \begin{tabular}{!{\vrule width 1.5pt}
        >{\columncolor{gray!30}}l
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}}
        \Xhline{1.5pt}
        \rowcolor{gray!30} 
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gWM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSMandWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSN$} \\
        \Xhline{1.5pt}
        $\gUNto$ & CE-\ref{CE:2} & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[1] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gNP$ & CE-\ref{CE:3} & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[1] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gMP$ & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[2] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gCR$ & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$ & $\gSN$ \\
        \Xhline{1.5pt}
    \end{tabular}
    \caption{Global implications}
\end{table}
\footnotetext[1]{This implication also requires $\gWCR$.}
\footnotetext[2]{This implication also requires either $\gWCR$ or the classical property required to go from 
$\SN \to \WN$ or $\SM \to \WM$.}
\renewcommand*{\thefootnote}{\arabic{footnote}}

@@

            % Sixth Counterexample - This one shows why UN -> doesn't imply UN
            \begin{minipage}{0.3\textwidth}
                \centering
                \begin{counterexample}\label{CE:un}
                    \begin{tikzcd}[row sep=small, column sep=small]
                        n & c \arrow[l] \arrow[r] & a \arrow[r, bend left] & b \arrow[l, bend left]
                        & d \arrow[l] \arrow[r] & m
                    \end{tikzcd} \\
                \end{counterexample}
            \end{minipage}
        % \\ % New row
        % \\
        &
        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:7}
            \begin{tikzcd}[row sep=small, column sep=small]
                f_0 \arrow[r] \arrow[dr] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[dl] \arrow[r] & \dots \arrow[dll] \\
                & n 
            \end{tikzcd} \\
            \end{counterexample}
        \end{minipage}
        \\ % new row
        \\

        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:8}
            \begin{tikzcd}[row sep=small, column sep=small]
                f_0 \arrow[r] \arrow[d] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[r] \arrow[d] & \dots \arrow[d] \\
                n_0  & n_1  & n_2 & \dots 
            \end{tikzcd} \\
            \end{counterexample}
        \end{minipage}

        &
        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:9}
            \begin{tikzcd}[row sep=small, column sep=small]
                a \arrow[r, bend left] & b \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    % \\ % New row
    % \\
    &
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:10}
            \begin{tikzcd}[row sep=small, column sep=small]
                d  \arrow[d] \arrow[rr, bend left] & a \arrow[r] \arrow[l]  &  
                b \arrow[r, bend left] & c \arrow[l, bend left] \\  
                f_0 \arrow[r] & f_1 \arrow[r] & f_2 \arrow[r] & \dots  
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    % New row
    \\
    \\
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:11}
            \begin{tikzcd}[row sep=small, column sep=small]
                c \arrow[r, bend left] & b \arrow[l, bend left]  & a \arrow[l] \arrow[r] 
                & d \arrow[r, bend left] & e \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    &
    &
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:12}
            \begin{tikzcd}[row sep=small, column sep=small]
                c & a \arrow[r, bend left] \arrow[l] & b \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}

>>>>

\begin{table}[h!]
    \centering
    \renewcommand\arraystretch{1.2}
    \begin{tabular}{!{\vrule width 1.5pt}
        >{\columncolor{gray!30}}l
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}}
        \Xhline{1.5pt}
        \rowcolor{gray!30} 
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SMandWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SN$} \\
        \Xhline{1.5pt}
        $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:11} & CE-\ref{CE:4} & CE-\ref{CE:6} & $\CR$\footnotemark[1] & CE-\ref{CE:8} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
        \hline
        $\NP$ & CE-\ref{CE:9} & CE-\ref{CE:8} & $\CR$ & CE-\ref{CE:6} & $\CR$\footnotemark[1] & CE-\ref{CE:8} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\MP$ & $\CR$ & CE-\ref{CE:8} & $\CR$ & CE-\ref{CE:6} & $\CR$\footnotemark[2] & CE-\ref{CE:8} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\CR$ & $\CR$ & CE-\ref{CE:8} & $\CR$ & CE-\ref{CE:6} & $\CR$ & CE-\ref{CE:8} & $\CR$ & $\SN$ & $\CR$ & $\SN$ \\
        \hline
        \Xhline{1.5pt}
    \end{tabular}
    \caption{Local implications}
\end{table}

\vspace{-1cm}
% \\[-0.5cm]
\begin{table}[h!]
    \centering
    \renewcommand\arraystretch{1.2}
    \begin{tabular}{!{\vrule width 1.5pt}
        >{\columncolor{gray!30}}l
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}}
        \Xhline{1.5pt}
        \rowcolor{gray!30} 
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gWM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSMandWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSN$} \\
        \Xhline{1.5pt}
        $\gUNto$ & CE-\ref{CE:2} & CE-\ref{CE:8} & $\gCR$ & CE-\ref{CE:6} & $\gCR$\footnotemark[1] & CE-\ref{CE:8} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gNP$ & CE-\ref{CE:3} & CE-\ref{CE:8} & $\gCR$ & CE-\ref{CE:6} & $\gCR$\footnotemark[1] & CE-\ref{CE:8} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gMP$ & $\gCR$ & CE-\ref{CE:8} & $\gCR$ & CE-\ref{CE:6} & $\gCR$\footnotemark[2] & CE-\ref{CE:8} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gCR$ & $\gCR$ & CE-\ref{CE:8} & $\gCR$ & CE-\ref{CE:7} & $\gCR$ & CE-\ref{CE:8} & $\gCR$ & $\gSN$ & $\gCR$ & $\gSN$ \\
        \Xhline{1.5pt}
    \end{tabular}
    \caption{Global implications}
\end{table}
\footnotetext[1]{This implication also requires $\gWCR$.}
\footnotetext[2]{This implication also requires either $\gWCR$ or the classical property required to go from 
$\SN \to \WN$ or $\SM \to \WM$.}
\renewcommand*{\thefootnote}{\arabic{footnote}}

@@

            % Sixth Counterexample - This one shows why UN -> doesn't imply UN
            \begin{minipage}{0.3\textwidth}
                \centering
                \begin{counterexample}\label{CE:5}
                    \begin{tikzcd}[row sep=small, column sep=small]
                        n & c \arrow[l] \arrow[r] & a \arrow[r, bend left] & b \arrow[l, bend left]
                        & d \arrow[l] \arrow[r] & m
                    \end{tikzcd} \\
                \end{counterexample}
            \end{minipage}
        % \\ % New row
        % \\
        &
        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:6}
            \begin{tikzcd}[row sep=small, column sep=small]
                f_0 \arrow[r] \arrow[dr] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[dl] \arrow[r] & \dots \arrow[dll] \\
                & n 
            \end{tikzcd} \\
            \end{counterexample}
        \end{minipage}
        \\ % new row
        \\

        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:7}
            \begin{tikzcd}[row sep=small, column sep=small]
                f_0 \arrow[r] \arrow[d] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[r] \arrow[d] & \dots \arrow[d] \\
                n_0  & n_1  & n_2 & \dots 
            \end{tikzcd} \\
            \end{counterexample}
        \end{minipage}

        &
        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:8}
            \begin{tikzcd}[row sep=small, column sep=small]
                a \arrow[r, bend left] & b \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    % \\ % New row
    % \\
    &
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:9}
            \begin{tikzcd}[row sep=small, column sep=small]
                d  \arrow[d] \arrow[rr, bend left] & a \arrow[r] \arrow[l]  &  
                b \arrow[r, bend left] & c \arrow[l, bend left] \\  
                f_0 \arrow[r] & f_1 \arrow[r] & f_2 \arrow[r] & \dots  
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    % New row
    \\
    \\
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:10}
            \begin{tikzcd}[row sep=small, column sep=small]
                c \arrow[r, bend left] & b \arrow[l, bend left]  & a \arrow[l] \arrow[r] 
                & d \arrow[r, bend left] & e \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    &
    &
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:11}
            \begin{tikzcd}[row sep=small, column sep=small]
                c & a \arrow[r, bend left] \arrow[l] & b \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
